Synthesis of Solar Photovoltaic Systems: Optimal Sizing Comparative\thanks{Supported by Newton Fund (ref. 261881580) and FAPEAM (Amazonas State Foundation for Research Support, calls 009/2017 and PROTI Pesquisa 2018).}

### 2020-01-08 Tex/CAV2019/Trindade_Cordeiro_CAV2020.tex
CAV 2020 paper update

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. To provide universal electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}. 
 Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}.

However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. Here, we use counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$. In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.

Related to past work, in $2012$, a Chinese smart grid implementation considered a case study to address the verification problem for performance and energy consumption~\cite{Yukseletall2012}. In $2015$, an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}. In $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}. Finally, in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}. However, prior studies did not deal with electricity generation or even solar PV systems optimization. Formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems are still unexplored in literature.

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented. Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) 
can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists and our synthesis engine can then conclude that no feasible equipment combination was found. At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.  %however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.
Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{Sharma14}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.4\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\
%
The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the items of each equipment and create a feasible solution.

The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements. Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.

Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

@@

Our synthesis algorithm was fed with data and costs of twenty-two equipment items from nine different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

\textbf{Setup.} All experiments were conducted on an otherwise idle Intel Xeon CPU E5-4617 (8-cores) with 2.90 GHz and 64 GB of RAM, running Ubuntu 16.04 LTS 64-bits. 
The experiments were performed with a predefined timeout of $240$ minutes.

@@

\textbf{Results.}  xxxxfalta as demais ferramentas????? CPAchecker was able to synthesize the optimal sizing of both case studies: the result was produced in $50.2$ and $37.2$ minutes, respectively. 
The violation of line 209 indicated in Table~\ref{tab1} is the $assert$ of line 22 from Algorithm~\ref{alg:verification-algorithm}. The results were tested by manual PV sizing and were sound (\textit{RQ1}). %, linking a feasible technical solution with the lowest cost possible, considering the equipment that were inputted to the code. 
CBMC and ESBMC produced \textit{UNKNOWN} result (\textit{timeout} or \textit{out of memory}); this partially answers the \textit{RQ2}.
%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.

\begin{table}[!t]
\caption{Case studies and results: optimization of PV systems.}\label{tab0}
\begin{tabular}{|c|c|c|c|c|}
\hline
\hline
Tools & \makecell{CPAchecker 1.8\\(MathSAT 5.5.3)}& CBMC & ESBMC & HOMER Pro 3.13.1\\
\hline
\hline
Specification & Result & Result & Result & Result \\
\hline
\makecell{\textbf{Case Study 1}\\Peak:342W\\Surge:342W \\E:3,900Wh/day\\Autonomy:48h} & \makecell{SAT (172.03 min) \\NTP:1$\times$340W (1S)\\NBT:8$\times$105Ah (2S-4P)\\Controller 15A/75V\\Inverter 700W/48V\\LCC: US\$ 7,790.53} & TO & TO & \makecell{(Time: 0.33 min)\\2.53 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.351kW inverter\\LCC: US\$ 7,808.04}\\
\hline
\makecell{\textbf{Case Study 2}\\Peak:814W\\Surge:980W\\E:4,880Wh/day\\Autonomy:48h} & \makecell {SAT (228.7 min) \\NTP:2$\times$330W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 20A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 8,335.90} & TO & TO & \makecell{(Time: 0.18 min)\\3.71 kW of PV\\NBT:20$\times$83.4Ah (2S-10P)\\0.817kW inverter\\LCC: US\$ 12,861.75} \\
\hline
\makecell{\textbf{Case Study 3}\\Peak:815W\\Surge:980W\\E:4,880Wh/day\\Autonomy:12h} & \makecell {SAT (166.13 min) \\NTP:4$\times$150W (4S)\\NBT:4$\times$80Ah (2S-2P)\\Controller 15A/100V DC\\Inverter 1,200W/24V \\LCC: US\$ 7,306.27} & TO & TO & Not possible \\
\hline
\makecell{\textbf{Case Study 4}\\Peak:253W\\Surge:722W\\E:3,600Wh/day\\Autonomy:48h} &  \makecell {SAT (143.71 min) \\NTP:4$\times$150W (4S)\\NBT:10$\times$80Ah (2S-5P)\\Controller 15A/75V\\Inverter 750W/24V \\LCC: US\$ 7,816.31} & TO & TO & \makecell{(Time: 0.23 min)\\2.42 kW of PV\\NBT:12$\times$83.4Ah (2S-6P)\\0.254kW inverter\\LCC: US\$ 7,677.95}\\
\hline
\makecell{\textbf{Case Study 5}\\Peak:263W\\Surge:732W\\E:2,500Wh/day\\Autonomy:48h} &  \makecell {SAT (134.93 min) \\NTP:1$\times$340W (1S)\\NBT:6$\times$105Ah (2S-3P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 7,252.14} & TO & TO & \makecell{(Time: 0.18 min)\\1.59 kW of PV\\NBT:10$\times$83.4Ah (2S-5P)\\0.268kW inverter\\LCC: US\$ 6,175.57} \\
\hline
\makecell{\textbf{Case Study 6}\\Peak:322W\\Surge:896W\\E:4,300Wh/day\\Autonomy:48h} &  \makecell {SAT (235.75 min) \\NTP:2$\times$200W (2S)\\NBT:10$\times$105Ah (2S-5P)\\Controller 15A/75V\\Inverter 400W/24V \\LCC: US\$ 8,287.23} & TO & TO & \makecell{(Time: 0.22 min)\\3.15 kW of PV\\NBT:14$\times$83.4Ah (2S-7P)\\0.328kW inverter\\LCC: US\$ 9,112.45} \\
\hline
\makecell{\textbf{Case Study 7}\\Peak:1,586W\\Surge:2,900W\\E:14,000Wh/day\\Autonomy:48h} & TO & TO & TO & \makecell{(Time: 0.20 min)\\12.5 kW of PV\\NBT:66$\times$83.4Ah (2S-33P)\\1.60kW inverter\\LCC: US\$ 41,878.11} \\
\hline
\hline
\end{tabular}
\\Caption: OM = out of memory; TO = timeout; IF = internal failure, E = energy.
\end{table}

>>>>

Lack of access to clean and affordable energy is considered a core dimension of poverty~\cite{Hussein2012}. Progress has been made worldwide; in particular, the number of people without electricity access fell below $1$ billion threshold for the first time in 2017~\cite{IEAweo2018}. To provide electricity for all, decentralized systems led by solar photovoltaic (PV) in off-grid and mini-grid systems will be the lowest-cost solution for three-quarters of the additional connections needed~\cite{Hussein2012}. %; specifically grid extension will be the standard in urban areas~\cite{IEAweo2018}.

In order to simulate or evaluate a PV system, there exist various specialized tools, e.g., RETScreen and HOMER~\cite{Pradhan,Swarnkar}%, PVWatts, SAM and Hybrid2 \cite{Pradhan,Swarnkar,NRELDobos,NRELBlair,Mills}
; and even general purpose simulation tools, e.g., MATLAB/Simulink~\cite{Gow1999}. %PSpice, Saber or MATLAB/Simulink package \cite{Gow1999,Benatiallah2017}.
 However, these tools are based on simulation; they have the drawback of an incomplete coverage  since verification of all possible combinations and potential failures of a system is unfeasible~\cite{ClarkeHV18}.

Optimization of PV systems is not a recent topic; since the 90's different techniques using different criteria to find ultimate combinations for design parameters, based on intuitive, numerical and analytical methods were proposed and developed~\cite{Alsadi2018}. %However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, which can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. 
Related to past work using formal methods based on \textit{symbolic model checking} and its application to electric systems: in $2015$ an automated simulation-based verification technique was applied to verify the correctness of power system protection settings~\cite{Sengupta2015}; in $2017$, a researcher suggested the application of formal methods to verify and control the behavior of computational devices in a smart grid ~\cite{Abate2017}; in $2018$, a verification methodology was applied to PV panels and its distributed power point tracking~\cite{Driouich2018}; and finally, in $2019$, an automated verification methodology was proposed to validate stand-alone solar PV systems~\cite{TrindadeCordeiro19}. However, formal methods and its application to synthesize PV systems are still unexplored in literature.

Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Note that in this study, our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods.

Our work makes two major contributions. Firstly, the use of automated symbolic verification in electrical systems was uncommon in recent prior studies~\cite{TrindadeCordeiro19}, and specifically their use in synthesizing PV sizing is unprecedented. %Here, a list of PV components %(i.e., PV panels, charge controllers, inverters, and batteries) can be fed to our proposed synthesis method together with user requirements and environment constraints, and our synthesis algorithm based on symbolic model checking can find the optimal solution in technical and economical terms. 
Secondly, we evaluate different state-of-art symbolic software verifiers with the goal of obtaining the best performance in our verification back-end for synthesizing optimal PV systems.

@@

In Figure~\ref{Counter-Example-Guided-Inductive-Synthesis}, the phases {\sc Synthesize} and {\sc Verify} interact via a finite set of test vectors {\sc inputs} that is incrementally updated. Given the correctness specification $\sigma$, the {\sc Synthesize} procedure tries to find an existential witness $\vec{F}$ satisfying the specification $\sigma(\vec{x}, \vec{F})$, for all $\vec{x}$ in {\sc inputs} (as opposed to all $\vec{x} \in \mathcal{D}$). If {\sc synthesize} succeeds in finding a witness~$\vec{F}$, the latter is a candidate solution (i.e., feasible combination of equipment) to the full synthesis formula, which is passed to {\sc verify}, in order to check whether it is a proper solution ({\it i.e.}, $\vec{F}$ satisfies the specification $\sigma(\vec{x}, \vec{F})$ for all $\vec{x}\in\mathcal{D}$). If this is the case, then the algorithm terminates, i.e., we have found a feasible equipment with the lowest cost; otherwise, additional information is provided to the phase {\sc synthesize}, in the form of a new counterexample that is added to the {\sc inputs} set and the loop iterates again. 
%
\begin{figure}[h]
	\centering
	\includegraphics[width=0.7\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
%
One may notice that each iteration of the CEGIS loop adds a new input to the finite set $INPUTS$, which is then used for synthesis.  Given that the full set of inputs $\mathcal{D}$ is finite because we use bit-vector expressions, this means that the refinement loop can only iterate over a finite number of times; however, {\sc synthesize} may conclude that no candidate solution obeying $\sigma$ for the finite set $INPUTS$ exists and our synthesis engine can then conclude that no feasible equipment combination was found. At this specific automated formal synthesis of PV systems, we use a variant of CEGIS, where in each iteration we increase the expected cost of PV systems and this controls the {\sc verify} phase and the search by the optimal sizing.  %however, $\mathcal{D}$ can represent a large number of elements for the finite set  and our synthesis engine can then conclude that no feasible equipment combination was found. 
%In order to avoid exploring all possible values, machine learning techniques can be used in the phase {\sc synthesize}, with the goal of learning from experience (input-output samples), {\it i.e.}, learning from counterexamples provided by a verification oracle~\cite{Alur13}. In addition to that, a pre-processing stage could also figure as another block in the scheme shown in Fig. \ref{Counter-Example-Guided-Inductive-Synthesis}, between {\sc verify} and {\sc synthesize}, which would process counterexamples and provide larger and refined information to the latter, according to specification $\sigma$ and domain $\mathcal{D}$, in order to speed-up convergence to a final candidate.

/////
Here, we have developed a variant of counterexample guided inductive synthesis (CEGIS) for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as a starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$, related to power reliability. In particular, in each iteration, we synthesize the sizing of stand-alone PV systems, but that may not achieve the lowest cost. The candidate solution is then verified via symbolic model checking with a lower bound that serves as the minimum cost of reference; if the verification step does not fail, the lower bound is adjusted. If it fails, then a counterexample is provided with an optimal sizing that meets both power reliability and system cost. Note that in this study, our focus is not on new criteria or even optimization objectives. Instead, our novelty relies on an effective approach to the pursuit of the optimal solution of PV systems using formal methods. 
////
Program synthesis engines that implement the CEGIS approach~\cite{sketch} can automatically produce solutions for a large variety of specifications, due to the combination of automated testing, genetic algorithms, and SMT-based reasoning~\cite{iet-cps.2018.5006}; here we have used software verifiers based on SMT solvers: %Here we used software model checking techniques implemented by different tools: 
CPAChecker~\cite{Beyer2011}, CBMC~\cite{Kroening}, and ESBMC~\cite{esbmc2018}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Sizing Stand-alone Solar PV Systems}
\label{sec:sizing}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
A PV system is illustrated in Fig.\ref{fig:blockdiagram}. %It identifies the PV generator, batteries, charge controller, inverter, and AC load. 
The PV generator, which can be a panel or an array, is a semiconductor device that can convert solar energy into DC electricity. %In Fig.\ref{fig:blockdiagram}, there are two variables that depend on the site where the system is deployed and also the weather (i.e., solar irradiance $G$ and temperature $T$). 
For night hours or rainy days, we hold batteries where power can be stored and used. The use of batteries as a storage form implies the presence of a charge controller~\cite{Hansen}. The PV arrays produce DC and therefore when the PV system contains an AC load, a DC/AC conversion is required. That converter is called inverter; and the AC load dictates the behavior of AC electrical load from the house that will be fed by the system.
\begin{figure}[h]
\includegraphics[width=0.7\textwidth]{blockdiagramPVS2_rev}
\centering
\caption{Block diagram for a typical stand-alone PV system~\cite{Hansen}.}
\label{fig:blockdiagram} 
\end{figure}
\\
%
The sizing check stage will ensure that the system meets the standard project steps related to critical period solar energy method~\cite{Pinho} and adopting MPPT (Maximum Power Point Tracking) charge controller, which is the most common one in practice. 
%
Firstly, we need to correct the energy consumption estimated to the load ($E_{consumption}$), which is carried out by Eq.~\ref{eq:Ecorrected}, where the efficiency of batteries ($\eta_{b}$), controller ($\eta_{c}$), and inverter ($\eta_{i}$) are considered~\cite{Pinho} as follows

@@

If our algorithm does not find a feasible solution among the item of equipment that were provided to our {\sc Synthesize} phase,  then the result is an unsatisfiable (\textit{UNSAT}), i.e., the program finishes and does not find a solution. It indicates that was not possible to combine the items of each equipment and create a feasible solution. The main challenge for the {\sc Synthesize} phase is to find a feasible candidate solution regarding the constraints and user requirements. Related to our {\sc Verify} phase the challenge is to find the lowest acquisition cost from a list of equipment and components that is provided from the {\sc Synthesize} phase.

%Note that the process described here in completely automated and that a validation is performed by our {\sc Verify} phase to ensure that the approach is sound.
%---------------------------------------------------------------------------
\section{Results and Discussion}
%---------------------------------------------------------------------------

@@

These case studies were defined based on usual electrical load found in riverside communities of the Amazon State in Brazil~\cite{TrindadeCordeiro19,Agrener2013}. With exception of case 7 that was idealized as a small town solution to support few lamps and an 12 kBTUs air-conditioner.

Our synthesis algorithm was fed with data and costs of forty equipment items from ten different manufacturers of PV systems. Furthermore, three start-of-art verification tools, CBMC,\footnote{Command-line: \$ cbmc -\phantom{}-unwind 100 filename.c -\phantom{}-trace} ESBMC,\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-boolector} %UAutomizer\footnote{Command-line: \$ ./Ultimate -tc config/AutomizerReach.xml -s config/svcomp-Reach-32bit-Automizer\_Default.epf -i filename.c -\phantom{}-traceabstraction.limit.analysis.time 900 -\phantom{}-traceabstraction.stop.after.first.violation.was.found false -\phantom{}-cacsl2boogietranslator.overapproximate.operations.on.floating.types false -\phantom{}- cacsl2boogietranslator.assume.nondeterminstic.values.are.in.range false -\phantom{}-rcfgbuilder.add.additional.assume.for.each.assert true -\phantom{}-rcfgbuilder.simplify.code.blocks true -\phantom{}-rcfgbuilder.size.of.a.code.block LoopFreeBlock}, 
and CPAchecker,\footnote{Command-line: \$ scripts/cpa.sh -heap 64000m -config config/bmc-incremental.properties -spec config/specification/sv-comp-reachability.spc filename.c} were used as our verification engine to compare our approach effectiveness and efficiency.

\textbf{Setup.} All experiments regarding the verification tools were conducted on an otherwise idle Intel Xeon CPU E5-4617 ($8$-cores) with $2.90$ GHz and $64$ GB of RAM, running Ubuntu $16.04$ LTS $64$-bits. Related to HOMER Pro, it was used an Intel Core i5-$4210$ ($4$-cores), with $1.7$ GHz and $4$ GB of RAM, running Windows 10. The experiments were performed with a predefined time out of $240$ minutes.

@@

\textbf{Results.}  CPAchecker was able to synthesize the optimal sizing in six out of seven case studies (cases $1$ to $6$): the result was produced within the time limit, which varied from $134.71$ to $235.75$ minutes. %Fig.~\ref{fig:CPAoptc1} illustrates the result of case 4 with the optimal sizing appearing in the left size as the integer $8$ to the solar panel (which is the model RSM36-6-150P from manufacturer Risen), battery $0$ that means the model 12MF80 of 80 Ah from Moura, charge controller $1$ that means the model 15A-75V MPPT from Victron  Energy, and the inverter number $3$ means the model IP350-11 from Epever (750 W). The variables NTP, NPS, NPP, NPS, NBP, and NBTotal, presented at the counter-example as well, shows how many and how the panels and batteries are connected.
Only case study $7$ led to a \textit{time out} result in CPAchecker, i.e., it was not solved within $240$ minutes. %However, if it is removed this time out limitation from CPAchecker, the verifier is able to solve the optimization in $44.97$ hours. 
The violation (SAT result) indicated in Table~\ref{tab1} 
is the $assert$ of line $22$ from Algorithm~\ref{alg:verification-algorithm}. CBMC and ESBMC are unable to produce any conclusive result. Situations of \textit{time out} or \textit{out of memory} occurred; this partially answers the \textit{EQ2} and \textit{EQ3}.

Related to HOMER Pro, it was able to evaluate six case studies (cases $1$, $2$, $4$, $5$, $6$, and $7$), and within a time shorter than $30$ seconds, which was much faster than the proposed automated synthesis tool (cf.~\textit{EQ2}). Case study $3$ was not possible to be simulated since HOMER Pro does not have the feature of adjusting the battery autonomy, i.e., the tool always tries to feed with electricity the given load during $365$ days/year.

Comparing the results between the formal synthesis with CPAchecker and HOMER Pro, it was observed that most results are quite similar, in terms of technical solution and cost (cf. Table~\ref{tab1}). Particularly related to LCC, the cost was very close in cases $1$, $4$, $5$ and $6$, with difference varying from $0.23$\% to $17.4$\%. Even adopting the same price per kW to the PV panels, inverters, and batteries, HOMER Pro does not use costs related to charge controllers, which were introduced into the CPAchecker modeling. The premise used in CPAchecker to adopt a fixed annual cost for operation and maintenance can produce some impact as well at this discrepancy; however, it is not significant since this annual cost is too small when compared to the resulting LCC value. However, there exists a huge divergence in case study $2$, where the costs presented by HOMER Pro were $54$\% higher than the automated synthesis tool, probably because the operation and maintenance costs assumed by the automated synthesis tool were underestimated to that specific load.

In general, the size of the PV panels and battery bank were bigger in HOMER Pro than with the formal synthesis approach, and that discrepancy is not easy to address without some real systems validation. Just to compare the results obtained from the optimization with the real-world, the authors had four PV systems deployed and monitored since June $2018$ in a riverside community in the Amazonas State in Brazil, with similar demands presented by case studies $1$, $4$, $5$, and $6$, always with a $3$ $\times$ $325$ W ($3$S) panels and $4$ $\times$ $220$ Ah ($2$S-$2$P $= 440$ Ah) lead-acid batteries. These solutions are more close to the result presented by the proposed formal synthesis approach than HOMER Pro, thereby showing that the solution is sound, which answers \textit{EQ1}.

Related to the inverters, HOMER Pro suggests a value in kW very close to the peak of every case study, and it is just a reference value and not a commercial value of the employed inverter. The proposed synthesis tool, however, presents inverters that are commercial and can be found off-the-shelf. Therefore is a PRO to the formal synthesis method.

Concerning to charge controllers, as it was reported in the  section~\ref{sec:synthesisresults}, HOMER Pro does not include it as an explicit equipment in its mathematical model, only the synthesis tool presents a commercial controller and includes it during the cost analysis. Therefore, the formal synthesis method presents more reliable results than HOME Pro.

Case study $7$ was not solved by the synthesis tool within the time limit established during the experimental phase. Case study $3$ was not possible to simulate in HOMER Pro, because its restriction does not allow one to set the battery autonomy, thus resting both without parameters to comparative.

\textbf{Conclusion.} Summarizing, the synthesis tool is capable to present a solution, which is far detailed and close to the commercial reality than the solution presented by HOMER Pro. In particular, the automated synthesis method can provide all the details of every component of a PV system solution, with complete electrical details from data sheet of manufacturers, including the model of the component, nominal current and voltage. In this respect, even the name of the manufacturer can be presented (in Table~\ref{tab1} it was removed to avoid some advertising).

%
%used with the SMT incremental mode\footnote{Command-line: \$ esbmc filename.c -\phantom{}-no-bounds-check -\phantom{}-no-pointer-check -\phantom{}-unwind 100 -\phantom{}-smt-during-symex -\phantom{}-smt-symex-guard -\phantom{}-z3} enabled with the goal of reducing memory usage; we have also used the SMT solver Z3 version 4.7.1~\cite{DeMoura}.
